\begin{frame}
    \begin{center}
        \LARGE \tt{Configuration}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Configure the External library}
    \begin{itemize}
        \item Some environment variables need to be
            set.
        \item For python, make sure {\tt pkg-config}
            can find python.
            \begin{itemize}
                \item {\tt pkg-config --cflags python}
                \item {\tt pkg-config --libs python}
                \item If some problems happens, check
                    the variable {\tt \$PKG\_CONFIG\_PATH}
            \end{itemize}
        \item For Boost, set variable {\tt \$BOOSTHOME}, and {\tt \$CPATH}.
            \begin{itemize}
                \item If you install Boost in {\tt \$DYB2External},
                    the {\tt \$BOOSTHOME} should be set to
                    {\tt \$DYB2External}.
                \item If the Boost libraries are found in 
                    {\tt /usr/lib}, the {\tt \$BOOSTHOME}
                    should be set to {\tt /usr}.
            \end{itemize}
        \item Here, the setup is complicated.
            We need to simplify this. (Please give comments.)
            \begin{itemize}
                \item Use a unified directory structure.
                \item Use unified environment variables.
                \item Separate external libraries from sniper.
                \item A good example: LCGCMT.
            \end{itemize}
    \end{itemize}
\end{frame}

% configure and compile sniper
\newsavebox{\installsniper}
\begin{lrbox}{\installsniper}
\begin{lstlisting}[language=bash]
$ cd $DYB2Area/sniper/SniperRelease/cmt/
$ cmt br cmt config
$ cmt br cmt make
$ source setup.sh
\end{lstlisting}
\end{lrbox}
% an example
\newsavebox{\testsniper}
\begin{lrbox}{\testsniper}
\begin{lstlisting}[language=bash]
$ cd $DYB2Area/sniper/Examples/HelloWorld/cmt
$ cmt config
$ cmt make
$ source setup.sh
$ cd ../share
$ python pyalg6.py
\end{lstlisting}
\end{lrbox}

\begin{frame}
    \frametitle{Configure the Sniper}
    \begin{itemize}
        \item If it is the first time to 
                use your sniper, you need to
                compile and setup it.
        \item The next time, only setup is needed.
    \end{itemize}
    \begin{block}{Configure and Compile}
        \par\usebox{\installsniper}
    \end{block}
    \begin{block}{A test}
        \par\usebox{\testsniper}
    \end{block}
\end{frame}

